FTLR proof cases

### 2018-03-09 fully-abstract-comp/ftlr-proof-cases.tex
TODO: xreadCond implies readcond.

\begin{lemma}[readXCondition implies readCondition]
  \label{lem:readXCond-readCond}
  If $\npair{(b,e)}\in\xReadCond{\lin,W}$, then $\npair{(b,e)}\in\readCond{\lin,W}$.
  \dominique{TODO}
\end{lemma}

>>>>

\begin{lemma}
  \label{lem:stareg-ms-subeq-stdreg}
  If
  \begin{itemize}
  \item $R \nequal \stareg[(\ms,\ms)]{\pur}$
  \item $\npair{(\ms,\ms)} \in H^{\mathrm{std}}_{\dom(\ms)} \; * \; W$
  \item $\dom(\ms) \supseteq [\baddr,\eaddr]$
  \end{itemize}
  Then
  $R \nsubeq \stdreg{\dom(\ms)}{\pur}$
\end{lemma}
\begin{proof}
  \dominique{TODO: define nsubeq and friends first?}
\end{proof}

\begin{lemma}[readXCondition implies readCondition]
  \label{lem:readXCond-readCond}
  If $\npair{(\baddr,\eaddr)}\in\xReadCond{\lin,W}$, then $\npair{(\baddr,\eaddr)}\in\readCond{\lin,W}$.
\end{lemma}
\begin{proof}
  From $\npair{(\baddr,\eaddr)}\in\xReadCond{\lin,W}$, we get by definition an $r \in \addressable{\lin, \pwheap}$ and an $\ms$ with $\dom(\ms) \supseteq [\baddr,\eaddr]$,  $\npair{(\ms,\ms)} \in H^{\mathrm{std}}_{\dom(\ms)} \; * \; W$ and $\pwheap(r) \nequal \stareg[(\ms,\ms)]{\pur}$.

  The result then follows directly using Lemma~\ref{lem:stareg-ms-subeq-stdreg}.
\end{proof}
